---
title: "French Lexicon Project: Shift Function and Stochastic Dominance Analysis"
output: html_notebook
---

Load packages and functions

```{r}
load("french_lexicon_project_rt_data.RData")
source("Rallfun-v35.txt")
source("wilcox_modified.txt")
source("rgar_visualisation.txt")
source("rgar_utils.txt")


library("tidyverse")
library("cowplot")
library("purrr")

```

Filter data and calculate deciles per participant

```{r}
P_Data_Non_Word <- filter(flp, condition %in% "non-word")
P_Data_Word <- filter(flp, condition %in% "word")

Word_Deciles <- do.call("rbind", tapply(P_Data_Word$rt, P_Data_Word$participant, quantile, seq(.1, .9, .1), type = 8))

Non_Word_Deciles <- do.call("rbind", tapply(P_Data_Non_Word$rt, P_Data_Non_Word$participant, quantile, seq(.1, .9, .1), type = 8))

Final_Word_Deciles <- c(t(Word_Deciles))
Final_Non_Word_Deciles <- c(t(Non_Word_Deciles))

Participants <- as.factor(rep(seq(1:967), each = 9))
Final_Df <- as.data.frame(cbind(Participants, Final_Non_Word_Deciles, Final_Word_Deciles))
```

Run shift function between deciles

```{r}
Shift_Fun <- shifthd(Non_Word_Deciles, Word_Deciles, nboot=200)

Shift_Fun
sf <- ggplot(Shift_Fun, aes(x=group1, y=group1-group2)) + 
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width=.1) +
    geom_line(linetype = 1, color = "green", size = 1.2) +
    geom_point(color="black", size=3) +
  ylim(-175, 175) +
  xlim(575, 1200)
sf + geom_hline(yintercept=0, linetype = "dashed") +
     theme_gray(base_size = 15) +
  xlab("Non-Word Deciles (ms)") + ylab("Non-Word - Word Deciles (ms)")
  
```

Create and run stochastic dominance function to test for positive or negative deciles differences within participants (1 = positive shift, 0 = negative shift). Then, test for any negative shifts to support hypothesis of a positive shift between congruent and incongruent deciles.

```{r}
Stoch_Dominance <- function(Vec_One) {
  SD <- sign(Vec_One)
  SD[SD == -1] <- 0
  return(as.data.frame(SD))
}

Decile_Differences <- Non_Word_Deciles - Word_Deciles
a <- as.vector(Stoch_Dominance(Decile_Differences))

x <- length(a[ a == 1 ])
y <- length(a[ a == 0 ])

x
y
```

Create regression function and run function over condition deciles for each participant. Then, test for any negative slopes between deciles to confirm hypothesis of a positive relationship between congruent and incongruent deciles.

```{r}
RaD <- function(x, y) {
  xy <- lm(x ~ y)
  co_eff <- sign(xy$coefficients[2])
  sumres <- summary(xy)
  p_res <- sumres$coefficients[2, 4]
  if (co_eff == -1 & p_res < 0.05) {
    print(0)
  } else if (co_eff == 1 & p_res < 0.05) {
    print(1) 
  } else {
    print("No Significant Relationship")
  }
}

Res <- by(Final_Df, Participants, 
   function(x) RaD(Final_Df$Final_Non_Word_Deciles, Final_Df$Final_Word_Deciles))

x <- as.vector(Res)
y <- x[x == 0]
y
```

Create correlation function and run function over condition deciles for each participant. Then, test for any negative correlations to support hypothesis of positive shift between congruent and incongruent deciles.

```{r}
Decile_Corr <- function(x, y) {
  xy <- cor(x, y, method = "spearman")
  if (xy < 0) {
    print(0)
  } else if (xy > 0) {
    print(1)
  } else {
    print("No Correlation")
  }
}

Res_Cor <- by(Final_Df, Participants, 
   function(x) Decile_Corr(Final_Df$Final_Non_Word_Deciles, Final_Df$Final_Word_Deciles))

a <- as.vector(Res_Cor)
b <- a[a == 0]
b

```
