---
title: "ManyLabs 3 Analysis: Shift Function and Stochastic Dominance Analysis"
output: html_notebook
---

Load data and packages

```{r}
source("Rallfun-v35.txt")
source("wilcox_modified.txt")
source("rgar_visualisation.txt")
source("rgar_utils.txt")
library("tidyverse")
library("cowplot")

Raw_Data <- read.csv("Stroop_Raw_Data.csv")

```

Filter data

```{r}
Congruent_Trials <- filter(Raw_Data, congruent %in% "Congruent")
Incongruent_Trials <- filter(Raw_Data,congruent %in% "Incongruent")

Congruent_Trials$session_id <- factor(Congruent_Trials$session_id)
Incongruent_Trials$session_id <- factor(Incongruent_Trials$session_id)


Congruent_Deciles <- do.call("rbind", tapply(Congruent_Trials$trial_latency, Congruent_Trials$session_id, quantile, seq(.2, .8, .1), type = 8))

Incongruent_Deciles <- do.call("rbind", tapply(Incongruent_Trials$trial_latency, Incongruent_Trials$session_id, quantile, seq(.2, .8, .1), type = 8))

Final_Congruent_Deciles <- c(t(Congruent_Deciles))
Final_Incongruent_Deciles <- c(t(Incongruent_Deciles))
Participants <- rep(seq(1:3337), each = 7)

Final_df <- as.data.frame(cbind(Participants, Final_Congruent_Deciles, Final_Incongruent_Deciles)) 

```

Run shift function between deciles

```{r}
Shift <- shifthd(Final_df$Final_Incongruent_Deciles, Final_df$Final_Congruent_Deciles, nboot=200)

sf <- ggplot(Shift, aes(x=group1, y=group1-group2)) + 
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width=.1) +
    geom_line(linetype = 1, color = "green", size = 1.2) +
    geom_point(color="black", size=3) +
  ylim(-150, 150) +
  xlim(450, 875)
sf + geom_hline(yintercept=0, linetype = "dashed") +
     theme_gray(base_size = 15) +
  xlab("Incongruent Deciles (ms)") + ylab("Incongruent - Congruent Deciles (ms)")

```

Create and run stochastic dominance function to test for positive or negative deciles differences within participants (1 = positive shift, 0 = negative shift). Then, test for any negative shifts to support hypothesis of a positive shift between congruent and incongruent deciles.

```{r}
Stoch_Dominance <- function(Vec_One) {
  SD <- sign(Vec_One)
  SD[SD == -1] <- 0
  return(as.data.frame(SD))
}

Decile_Differences <- Final_Incongruent_Deciles - Final_Congruent_Deciles
a <- as.vector(Stoch_Dominance(Decile_Differences))

x <- length(a[ a == 1 ])
y <- length(a[ a == 0 ])

x
y
```


Create regression function and run function over condition deciles for each participant. Then, test for any negative slopes between deciles to confirm hypothesis of a positive relationship between congruent and incongruent deciles.

```{r}
RaD <- function(x, y) {
  xy <- lm(x ~ y)
  co_eff <- sign(xy$coefficients[2])
  sumres <- summary(xy)
  p_res <- sumres$coefficients[2, 4]
  if (co_eff == -1 & p_res < 0.05) {
    print(0)
  } else if (co_eff == 1 & p_res < 0.05) {
    print(1) 
  } else {
    print("No Significant Relationship")
  }
}

Regression <- by(Final_df, Participants, 
   function(x) RaD(Final_df$Final_Congruent_Deciles, Final_df$Final_Incongruent_Deciles))

as.vector(Regression)
y <- Regression[Regression == 0]
y
```

Create correlation function and run function over condition deciles for each participant. Then, test for any negative correlations to support hypothesis of positive shift between congruent and incongruent deciles.

```{r}
Decile_Corr <- function(x, y) {
  xy <- cor(x, y, method = "spearman")
  if (xy < 0) {
    print(0)
  } else if (xy > 0) {
    print(1)
  } else {
    print("No Correlation")
  }
}

Correlation <- by(Final_df, Participants, 
   function(x) Decile_Corr(Final_df$Final_Congruent_Deciles, Final_df$Final_Incongruent_Deciles))

as.vector(Correlation)
x <- Correlation[Correlation == 0]
x


```

